\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Mahdi Amoozadeh}}
\end{center}

\begin{center}
    \small{
    +98-9125090894 | \href{mailto:mahdi.am6@gmail.com}{mahdi.am6@gmail.com} 
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://ir.linkedin.com/in/mahdi-amoozadeh-445a58b4}{Mahdi Amoozadeh} | 
    \socialicon{\faGithub} \href{https://github.com/Mapl6}{Mapl6} 
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Tehran , Iran}
\end{center}

\vspace{-4mm}

\section{\textbf{ABOUT ME}}
\vspace{1mm}
\small{
I'm a highly motivated mid-level Frontend Developer with over two years of experience building responsive, user-friendly web applications. I started coding as a hobby in 2016, and in 2022, I began focusing on JavaScript and frontend development.

Since then, I’ve worked on many freelance projects. I care a lot about clean UI, good performance, and simple user experiences.

Right now, I’m working at Tavana, where I’ve grown as both a developer and a teammate—going deeper into the React ecosystem and getting better at using Next.js, Tailwind, and team workflows.
}

\vspace{6mm}
\section{\textbf{Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
    {{Tavana [\href{https://tavanastore.ir/}{\faIcon{globe}}]}}{Tehran, Iran}
    {Frontend Developer}{November 2024 – Present}
    \resumeItemListStart
        \item Improved my teamwork skills and learned to work better in a team environment.
        \item Got deeper experience with Next.js and modern frontend tools.
        \item Helped build and improve fast, scalable components for an online store.
    \resumeItemListEnd
    \vspace{2mm}

\resumeSubheading
  {Tavana Store (E-commerce Platform):}{} 
  {Tools: Next.js 14, Tailwind CSS, i18n, Swiper.js}{Tavana}
  \item Refactored the whole Tavana Store website to make it faster, easier to manage, and better for users.
  \item Added multi-language support (i18n) so users can switch between different languages.
  \item Used Swiper.js and Tailwind to improve design and make sliders more responsive on all devices.


    \vspace{10mm}

  \resumeSubheading
      {{Bluprint [\href{https://bluprint.ir/}{\faIcon{globe}}]}}{Tehran, Iran}
      {Frontend Developer}{March 2024 - November 2024}
      \resumeItemListStart
      \vspace{6mm}
During my time at this company, I faced challenges like learning \textbf{React Native}, \textbf{Redux}, and \textbf{Zustand}, and successfully completed \textbf{five projects}, with three currently active. Key projects include:
      \resumeItemListEnd 
      \vspace{2mm}
\resumeSubheading  {Pax Cast:}{}
{tools:}{Bluprint} 
  \item  A platform for medical imaging centers where patients can view images and reports, and centers can manage their services easily.

\resumeSubheading {Marvel Quiz:} {}
{tools:}{Bluprint} 

  \item A quiz platform where users can browse and buy exams, upload PDFs, add questions, and review answers. Exams can have multiple booklets with online answer sheets.


\resumeSubheading {One Coach:} {}
{tools:}{Bluprint} 

  \item A web app for coaches and trainees. Coaches can manage training sessions, and trainees can view exercises, watch videos, and mark sessions complete.


\resumeSubheading {VPN Client:} {}
{tools:}{Bluprint} 

  \item A mobile app for secure VPN connections using manual settings or QR codes.


\resumeSubheading {Trust Pilot (Iranian Version):}{}
{tools:}{Bluprint} 
\item A platform to find, review, and rate businesses, and read others’ reviews.

 \vspace{6mm}
These projects helped me improve my technical skills .


\vspace{6mm}

\section{\textbf{Freelance Projects}}
\vspace{-0.4mm}


\resumeSubheading
     {Parsian Refinery [\href{http://parsianrefinery.com}{\faIcon{globe}}]}{2024}
     {Tools: Next.js, Framer Motion, Tailwind CSS, Swiper.js}
     {}

 \resumeSubheading
  {Vitrine [\href{https://vitrin.semnan.ac.ir}{\faIcon{globe}}]}{2022}
  {Tools: React.js, Swiper.js}
{}
\resumeSubheading
    {Satyar Sanat Novin Oxin [\href{https://ssnoc.com/}{\faIcon{globe}}]}{2023}
    {Tools: TypeScript, Next.js, Tailwind CSS, Framer Motion, i18next}
    {}
 \resumeSubheading
  {Invoice Generator (Hesabemoon) [\href{https://hesabemoonv2.vercel.app/home}{\faIcon{globe}}]}{2022}
  {Tools: Next.js, Framer Motion}
{}
 \resumeSubheading
  {Print House [\href{https://print-house.vercel.app}{\faIcon{globe}}]}{2023}
  {Tools: Next.js, Framer Motion, Swiper.js}
  {}
 \resumeSubheading
  {Phishing Detector Chrome Extension}{2023}
  {Tools: HTML, CSS}
  {}
\resumeItemListStart
  \item Developed a Chrome extension to assess phishing risk on opened websites
  \item Implemented visual indicators and alerts to warn users of potential threats
  \item Designed the extension with HTML and CSS for a user-friendly interface
\resumeItemListEnd

 \resumeSubheading
  {DNS Dashboard}{2023}
  {Tools: react, pure CSS}
  {}
\resumeItemListStart
  \item Developed a comprehensive dashboard to monitor and manage DNS settings
  \item Created interactive features for managing DNS records, enhancing user control
  \item Utilized a clean, intuitive layout for efficient data visualization
\resumeItemListEnd

\resumeSubHeadingListEnd
\section{\textbf{Education}}
\vspace{-0.4mm}
\begin{itemize}[left=0mm, label={}]
    \item \textbf{Semnan University}, Semnan, Iran \\
    Bachelor’s Degree in Computer Science \hfill 2017 – 2022
    \vspace{2mm}
    \item \textbf{Azad University}, Tehran, Iran \\
    Master’s Degree in Software Engineering \hfill 2023 – Current
\end{itemize}

\section{\textbf{Skills}}
\vspace{-0.4mm}
\resumeHeadingSkillStart

\resumeSubItem{Fundamentals:}
  {HTML, CSS, JavaScript, Responsive Design}
\resumeSubItem{Frontend Frameworks:}
  {Next.js,React.js}
\resumeSubItem{State Management:}
  {Zustand,Redux, Redux Toolkit, Redux DevTools}
\resumeSubItem{CSS Frameworks:}
  {Tailwind CSS}
\resumeSubItem{Version Control:}
  {Git, GitHub, GitLab}
\resumeSubItem{Other Tools \& Libraries:}
  {REST API, NextUI, Material UI, i18next, Framer Motion,Swiper js,React Hook Form}

\resumeHeadingSkillEnd

\section{\textbf{Certifications}}
\vspace{-0.2mm}
\resumeSubHeadingListStart
\resumePOR
    {Quera Front-End Bootcamp}
    {}
{{[\href{https://quera.org/media/public/quera_certificate/0669e232806f46ea83cdae4217677549.jpg}{\faIcon{globe}}]}}
\resumeSubHeadingListEnd



\section{\textbf{Languages}}
\vspace{-0.4mm}

\textbf{Mother Tongue:} Persian \\
\begin{itemize}
  \item \textbf{English:} Independent User \begin{itemize}
      \item Listening: B1
      \item Reading: B2
      \item Writing: B1
      \item Spoken Production: B1
      \item Spoken Interaction: B1 \end{itemize}
\end{itemize}

\vspace{-4mm}
\end{document}chat
